### 2016-04-15 ch04-lrmhinf/lrmhinf.tex
Small changes here and there
Some small things

@@

The parametrization of the plant model set $\ModelSet[]$ conforms to the dual-\YK{} framework~\citep{Hansen1989,Anderson1998} that parametrizes $\ModelSet[]$ in terms of  all plants $P$ that are stabilized by the controller $C$:
\begin{equation}
  \ModelSet[] 
    \isdef 
      \Set{
            \frac{\hat{N} + D_c \Delta}
                 {\hat{D} - N_c \Delta} 
          |
            \hinfnorm{\Delta} \leq \gamma
        }
  \label{eq:lrmhinf:dualYoulaModelSet}
  \text{,}
\end{equation}
where $C=N_c D_c^{-1}$ and $\estimated\Plant = \estimated{N}\estimated{D}^{-1}$ are decomposed as \gls{RCF} (see \figref{fig:lrmhinf:dualYoula}).
To estimate $\Delta$ and $\hinfnorm{\Delta}$, the signals $u_{\Delta}$ and $y_{\Delta}$ in~\figref{fig:lrmhinf:dualYoula} are required.
These can be computed from $u$ and $y$ directly~\citep{Anderson1998}.
%TODO{formules Hansen schema}
In addition, $u_{\Delta}$ is noise free under standard assumptions~\citep{Hansen1989}, hence the method of \secref{sec:lrmhinf:LPMHinf} applies directly.

>>>>

%TODO: The quality of the estimate of the H-infinity norm of Delta is completely unknown. In other words, there is no theoretical guarantee about the error. --> Tom: addresseren. Feitelijk hangt dit samen met de kwaliteit van standaard lpm/lrm, toch?

@@

The parametrization of the plant model set $\ModelSet[]$ conforms to the dual-\YK{} framework~\citep{Hansen1989,Anderson1998} that parametrizes $\ModelSet[]$ in terms of  all plants $P$ that are stabilized by the controller $C$:
\begin{equation}
  \ModelSet[] 
    \isdef 
      \Set{
            \frac{\hat{N} + D_c \Delta}
                 {\hat{D} - N_c \Delta} 
          |
            \hinfnorm{\Delta} \leq \gamma
        }
  \label{eq:lrmhinf:dualYoulaModelSet}
  \text{,}
\end{equation}
where $C=N_c D_c^{-1}$ and $\estimated\Plant = \estimated{N}\estimated{D}^{-1}$ are decomposed as \gls{RCF} (see \figref{fig:lrmhinf:dualYoula}).
To estimate $\Delta$ and $\hinfnorm{\Delta}$, the signals $u_{\Delta}$ and $y_{\Delta}$ in~\figref{fig:lrmhinf:dualYoula} are required.
These can be computed from $u$ and $y$ directly~\citep{Anderson1998}:
\begin{align}
  u_{\Delta}(t) &= \left(\hat{D} + C \hat{N} \right)^{-1} \mat{C & \I} \mat{y(t)\\u(t)}\\
  y_{\Delta}(t) &= \left(D_c + \hat{P} N_c \right)^{-1} \mat{\I & -\hat{P}} \mat{y(t)\\u(t)}
\end{align}
In addition, $u_{\Delta}$ is noise free under standard assumptions~\citep{Hansen1989} and uncorrelated to $y_{\Delta}$. 
Hence the method of \secref{sec:lrmhinf:LPMHinf} applies directly.

### 2016-04-15 ch05-initvals/initial-values.tex
Some small things

\item \emph{Local polynomial method (LPM) with truncation}

A good estimate of the \gls{FRF} of the chosen system can be obtained via the truncated \gls{LPM}, which is summarized as follows~\citep{Lumori2014TIM} and \secref{sec:nonparametric:truncation} of this thesis.
Here, we repeat the main points briefly.
The \gls{LPM} is first applied to estimate the \gls{FRF} from a full input/output data record of the \gls{SISO} system.
The smooth characteristics of both the exact \gls{FRF} $\true{G}$ and the transient term $T$ allow for application of the \gls{LPM}, leading to a smooth \gls{FRF} estimate with the transient and noise suppressed.

  With reference to a detailed exposition in~\citep{Lumori2014TIM} and \chapref{sec:nonparametric}, the \gls{LPM} utilizes local polynomials to approximate the transfer function and transient contribution (in least squares sense) and, thus, smooth $\true{G}$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$.
  In this chapter, we limit the notations to quadratic polynomials in a window with half-width $n=3$, such that
\begin{subequations}\label{lpmImplQuadG}
\begin{align}
\true{G}(\Omega_{k+r})&\approx \hat G_k + g_{1,k} r + g_{2,k}r^2
\\
T(\Omega_{k+r})&\approx T(\Omega_k)+t_{1,k}r + t_{2,k}r^2\label{lpmImplQuadT}
\end{align}
\end{subequations}
where, in general,$\ r\in \LocalShifts[]$ with $\LocalShifts[] = \{-n,-n+1,\dots,n\}$ and $n$ is a tunable parameter. 
\TODO{notatie LPM uniform maken met CH03/CH04}

  The \gls{LPM} estimate of the \gls{FRF} at frequency index $k$ is the first estimated local parameter, \emph{viz}:
\begin{equation}
\hat{G}_\text{poly}(\Omega_k) = \hat{G}_k
\text{.}
\end{equation}
This procedure is repeated for all $k$ in the frequency band of interest.

\emph{Impulse response truncation}. 
The estimate is smoothed further by truncating its impulse response function $g_{\text{poly}}(t) = \mathrm{IDFT}\, \left( \hat{G}_\text{poly}(\Omega_k)) \right)$ as originally presented in~\citep{Lumori2014TIM} and \secref{sec:nonparametric:truncation}.

The impulse response is truncated after the time $\truncTime$ where the signal becomes indistinguishable from the noise, i.e.,
\begin{equation}
  g_{\mathrm{trunc}}(t) = 
  \begin{cases}
    g_{\text{poly}}(t) & t \leq \truncTime \\
    0                              & t \geq \truncTime
  \end{cases}
  \text{.}
\end{equation}

To this end, an estimate of the envelope of impulse response is determined by fitting an exponential function $g_{\mathrm{exp}}(t) = B e^{\beta t}$ to the peaks of $\abs{g_{\mathrm{poly}}(t)}$ using a linear least-squares approach.
Then, $\truncTime$ is determined as the time instant where this envelope function sinks below the noise level $\sigma_g$ of the impulse response, i.e. 
\begin{equation}
  \truncTime = \min \Set{ t :  g_{\mathrm{exp}}(t) < \gamma \sigma_g  }
  = \beta^{-1} \ln \frac{\gamma \sigma_g}{B}
  \text{,}
\end{equation}
where $\gamma=1$ was used in this chapter for simplicity.
By changing $\gamma$, the user can fine-tune the bias/variance trade-off of the estimated \gls{FRF} $G_{\mathrm{trunc}}(\Omega_k) = \mathrm{DFT} \left( g_{\mathrm{trunc}}(t)\right)$ further.
This can lead to a significant improvement over the classical LPM~\citep{Lumori2014TIM}.

>>>>

\item \emph{Local polynomial method (LPM) with truncation}
\disclaimer{The time-truncated \gls{LPM} has been explained in \secref{sec:nparam:trunc} in more detail. The pertinent details are repeated here to aid readability.}
A good estimate of the \gls{FRF} of the chosen system can be obtained via the truncated \gls{LPM}, which is summarized as follows~\citep{Lumori2014TIM} and \secref{sec:nonparametric:truncation} of this thesis.
Here, we repeat the main points briefly.
The \gls{LPM} is first applied to estimate the \gls{FRF} from a full input/output data record of the \gls{SISO} system.
The smooth characteristics of both the exact \gls{FRF} $\true{G}$ and the transient term $T$ allow for application of the \gls{LPM}, leading to a smooth \gls{FRF} estimate with the transient and noise suppressed.

  With reference to a detailed exposition in~\citep{Lumori2014TIM} and \chapref{sec:nonparametric}, the \gls{LPM} utilizes local polynomials to approximate the transfer function and transient contribution (in least squares sense) and, thus, smooth $\true{G}$ and $T$ around a central frequency $\Omega_{k}$ in a local frequency band $r\in\mathbb{W}_n$.
  In this chapter, we limit the notations to quadratic polynomials in a window with half-width $N_W=3$, such that
\begin{subequations}\label{lpmImplQuadG}
\begin{align}
\true{G}(\Omega_{k+r})&\approx \hat G_k + g_{1,k} r + g_{2,k}r^2
\\
T(\Omega_{k+r})&\approx T(\Omega_k)+t_{1,k}r + t_{2,k}r^2\label{lpmImplQuadT}
\end{align}
\end{subequations}
where, in general,$\ r\in \LocalShifts[]$ with $\LocalShifts[] = \{-N_W,-N_W+1,\dots,B_W\}$ and $N_W$ is a tunable parameter. 
%TODO notation LPM uniform maken met CH03/CH04

  The \gls{LPM} estimate of the \gls{FRF} at frequency index $k$ is the first estimated local parameter, \emph{viz}:
\begin{equation}
\hat{G}_\text{LPM}(\Omega_k) = \hat{G}_k
\text{.}
\end{equation}
This procedure is repeated for all $k$ in the frequency band of interest.

\emph{Impulse response truncation}. 
The estimate is smoothed further by truncating its impulse response function $g_{\LPM}(t) = \mathrm{IDFT}\, \left( \hat{G}_{\LPM}(\Omega_k)) \right)$ as originally presented in~\citep{Lumori2014TIM} and \secref{sec:nonparametric:truncation}.

The impulse response is truncated after the time $\truncTime$ where the signal becomes indistinguishable from the noise, i.e.,
\begin{equation}
  g_{\trunc}(t) = 
  \begin{cases}
    g_{\LPM}(t) & t \leq \truncTime \\
    0                              & t \geq \truncTime
  \end{cases}
  \text{.}
\end{equation}

To this end, an estimate of the envelope of impulse response is determined by fitting an exponential function $g_{\mathrm{exp}}(t) = B e^{\beta t}$ to the peaks of $\abs{g_{\LPM}(t)}$ using a linear least-squares approach.
Then, $\truncTime$ is determined as the time instant where this envelope function sinks below the noise level $\sigma_g$ of the impulse response, i.e. 
\begin{equation}
  \truncTime = \min \Set{ t :  g_{\mathrm{exp}}(t) < \gamma \sigma_g  }
  = \beta^{-1} \ln \frac{\gamma \sigma_g}{B}
  \text{,}
\end{equation}
where $\gamma=1$ was used in this chapter for simplicity.
By changing $\gamma$, the user can fine-tune the bias/variance trade-off of the estimated \gls{FRF} $G_{\trunc}(\Omega_k) = \mathrm{DFT} \left( g_{\trunc}(t)\right)$ further.
This can lead to a significant improvement over the classical LPM~\citep{Lumori2014TIM}.
